Modelling the Retinotectal projection - can competition provide a stopping mechanism?

### 2021-02-03 paper/notes.tex
WIP on the blowup problem

>>>>

\emph{January 2021.} I did a lot of work on the visualisation code, making it a lot
faster. This allowed me to get to the bottom of the blow up. The culprit is
$\hat{a}$ and its divergence. There's a positive feedback loop here. I don't
think this invalidates the model of using the gradient of $\hat{a}$ as
competition, because in a real, biological system, $a$, and hence $\hat{a}$
are bounded by finite resources. I'm thus going to allow bounding of $a_i$.
